Design of Blur Invariant Fiducial for Low Cost Quadcopter

### 2014-02-03 ECCV/paper.tex
Few more related work.

\section{Related Work}
ARToolkit \cite{ARToolkit02} /ARTag \cite{Fiala05} \\
Pi-Tag \cite{Pitag13} \\
Blut \cite{Wu:2011}

>>>>

\section{Related Work}
ARToolkit \cite{ARToolkit02} /ARTag \cite{Fiala05} \\
Circular Data Matrix Fiducial System \cite{NaimarkF02}
Reliable Fiducial Detection in Natural Scenes \cite{ClausF04}
RUNE-Tag \cite{runetag11}
Pi-Tag \cite{Pitag13} \\
Blut \cite{Wu:2011}
